---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# susolisting shiny application

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This application is part of the large set of tools, to facilitate survey implementation with
[Survey Solutions](https://docs.mysurvey.solutions/). Enumeration Areas, sampled for example
with the JDC-Survey Solutions Spatial Sampling application, can be used to enumerate all buildings
visible within the boundaries on a google map. The enumerate buildings can then be used for the
second stage sampling frame and to draw the survey units within the cluster from it.

## Installation

* Install R: https://cran.r-project.org/mirrors.html (version 4.1.1 or greater)

* Install R Studio: https://rstudio.com/products/rstudio/download/ (version 1.2.5001-3 or newer)

* Make sure the *devtools* package is installed, if not install it with:

```{r devtoolsinst,eval=FALSE, echo=TRUE}
install.packages("devtools")

```


* After that install the actual package:

```{r install,eval=FALSE, echo=TRUE}
devtools::install_github("michael-cw/susolisting")

```

## Start the application

```{r start, eval=FALSE, echo=TRUE}
library(susolisting)
susolisting::runListingApp()

```

